Investigation of Multi-Angle Detection Schemes for Light Scattering of Optically Trapped Asymmetric Colloidal Particles

### 2024-05-20 Latex_files/Manuscripts Scattering/Manuscript_Optica.tex
09:31 20-05-24

\documentclass[preprint,  3p]{elsarticle}

\usepackage{csvsimple}
\usepackage{amssymb, amsthm}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{lineno}
\usepackage{color}
\usepackage{nomencl}
\usepackage{tabularx}
\makenomenclature
\renewcommand{\nomlabel}[1]{\hfil #1\hfil}

\journal{}

@@

\begin{frontmatter}

@@

\author[aff1]{Daniel Maciver\corref{cor1}} 
\ead{Daniel.Maciver.2016@uni.strath.ac.uk}

\author[aff1]{Praveen Parthasarathi}

\author[aff1]{Leo Lue}

\author[aff1]{Jan Sefcik}

\author[aff1]{Mark Haw}

\cortext[cor1]{Corresponding author}
\affiliation[aff1]{organization={Department of Chemical Engineering,
			University of Strathclyde},
            addressline={75 Montrose Street}, 
            city={Glasgow},
            postcode={G1 1XL}, 
            country={Scotland}}
\begin{abstract}
  % \justifying
  %
  Optical trapping is a well understood method for transduction and detection
  of forces on trapped colloidal particles, these trapped entities can be
  further characterised using light-scattering, posing a two-fold challenge:
  one experimental, concerning the optimal arrangement of detectors to gather
  data and minimise signal noise, and the other theoretical, involving solving
  of the inverse scattering problem in order to interpret light scattering
  data to determine size, shape, or orientation of the trapped object.
  Experimentally, combining static light scattering techniques with optical
  trapping poses significant engineering challenges due to the space
  constraints in a conventional optical trapping setup. We investigated a
  plausible scenario of detecting scattered light from an optically trapped
  asymmetric particles using a novel, multi-angle, optical-fibre based
  detection scheme, we show how a Bayesian inference-based analysis of the
  data, combined with a neural-network trained on data simulated to mimic
  light scattering detection signals in such scenarios, can be used for
  solving the inverse light scattering problem and characterising colloidal
  trapped entities. To demonstrate the method, we discuss its application to
  measuring the instantaneous orientations of a trapped asymmetric microsphere
  dimer and determine the minimum number of detectors required for a reliable
  estimation in the presence of signal noise. This approach can be extended to
  determine any characteristics of the trapped microstructure that influence
  the light scattering pattern, including size and shape of colloidal objects. 
\end{abstract}

@@

\begin{keyword}
	Optical Trapping \sep Light Scattering \sep Measurements \sep Bayesian Statistics 
\end{keyword}

\end{frontmatter}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:A1}
		%
		Reference Orientations vector components, for $n_{refs} = 30 \ ^*$}
		\begin{tabularx}{0.65\textwidth}{
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X | }
			\hline\hline
			$\alpha$ & $\hat{\bf n}_{\alpha,\ x}$ &  $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ 
			\\ \hline
			\csvreader[
			head to column names
			]
			{./data/n_list.csv}{}{
			\index\ & \nx\ & \ny\ & \nz\ \\
			} \\
			\hline\hline 
		\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabularx}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:A2}
			% 
			Raw intensities $I_k^*$ and scaled intensities $y_k$}
		\begin{tabular}{|c|c|c|c|c|c|c|}
			\hline\hline
			$\alpha$  & $I(\hat{\bf n}_\alpha\ ,\ 15^{\circ})$ &  $I(\hat{\bf n}_\alpha \ , \ 55^{\circ})$ &  $I(\hat{\bf n}_\alpha \ ,\ 90^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 15^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 55^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 90^{\circ})$ \\
		    \hline
			\csvreader[
			head to column names
			]
			{./data/y_list.csv}{}{
				\index\ & \Ix\ & \Iy\ & \Iz\ & \yx\ & \yy\ & \yz\ \\
			} \\
			\hline\hline 
			\multicolumn{7}{l}{\small *$I_k$ values are calculated using MSTM package.} \\
		\end{tabular}
	\end{center}
\end{table}

>>>>

\documentclass[12pt]{optica-article}

\usepackage{csvsimple}
\usepackage{lineno}

\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{lineno}
\usepackage{color}
\usepackage{nomencl}
\usepackage{tabularx}
\makenomenclature
\renewcommand{\nomlabel}[1]{\hfil #1\hfil}
\linenumbers

\journal{opticajournal}

@@

%\begin{frontmatter}

@@

\author{Daniel Maciver, \authormark{1,*}, Praveen Parthasarathi, \authormark{1}, Leo Lue, \authormark{1}, Jan Sefcik, \authormark{1},
Mark Haw, \authormark{1}}

\address{\authormark{1}Department of Chemical Engineering,
	University of Strathclyde, 75 Montrose Street, Glasgow,
	G1 1XL, Scotland}
\email{\authormark{*}daniel.maciver.2016@uni.strath.ac.uk}

\begin{abstract}
  % \justifying
  %
  Optical trapping is a well understood method for transduction and detection
  of forces on trapped colloidal particles, these trapped entities can be
  further characterised using light-scattering, posing a two-fold challenge:
  one experimental, concerning the optimal arrangement of detectors to gather
  data and minimise signal noise, and the other theoretical, involving solving
  of the inverse scattering problem in order to interpret light scattering
  data to determine size, shape, or orientation of the trapped object.
  Experimentally, combining static light scattering techniques with optical
  trapping poses significant engineering challenges due to the space
  constraints in a conventional optical trapping setup. We investigated a
  plausible scenario of detecting scattered light from an optically trapped
  asymmetric particles using a novel, multi-angle, optical-fibre based
  detection scheme, we show how a Bayesian inference-based analysis of the
  data, combined with a neural-network trained on data simulated to mimic
  light scattering detection signals in such scenarios, can be used for
  solving the inverse light scattering problem and characterising colloidal
  trapped entities. To demonstrate the method, we discuss its application to
  measuring the instantaneous orientations of a trapped asymmetric microsphere
  dimer and determine the minimum number of detectors required for a reliable
  estimation in the presence of signal noise. This approach can be extended to
  determine any characteristics of the trapped microstructure that influence
  the light scattering pattern, including size and shape of colloidal objects. 
\end{abstract}

@@

%\begin{keyword}
%	Optical Trapping \sep Light Scattering \sep Measurements \sep Bayesian Statistics 
%\end{keyword}

%\end{frontmatter}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:A1}
		%
		Reference Orientations vector components, for $n_{refs} = 30 \ ^*$}
		\begin{tabularx}{0.9\textwidth}{
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X | }
			\hline\hline
			$\alpha$ & $\hat{\bf n}_{\alpha,\ x}$ &  $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ 
			\\ \hline
			$1$ & $0.2958759$ & $0.2958759$ & $0.9082483$ \\
			$2$ & $0.9082483$ & $0.2958759$ & $0.2958759$ \\
			$3$ & $0.2958759$ & $0.9082483$ & $0.2958759$ \\
			$4$ & $0.2958759$ & $0.2958759$ & $-0.9082483$ \\
			$5$ & $0.9082483$ & $0.2958759$ & $-0.2958759$ \\
			$6$ & $0.2958759$ & $0.9082483$ & $-0.2958759$ \\
			$7$ & $0.2958759$ & $-0.2958759$ & $0.9082483$ \\
			$8$ & $0.9082483$ & $-0.2958759$ & $0.2958759$ \\
			$9$ & $0.2958759$ & $-0.9082483$ & $0.2958759$ \\
			$10$ & $0.2958759$ & $-0.2958759$ & $-0.9082483$ \\
			$11$ & $0.9082483$ & $-0.2958759$ & $-0.2958759$ \\
			$12$ & $0.2958759$ & $-0.9082483$ & $-0.2958759$ \\
			$13$ & $-0.2958759$ & $0.2958759$ & $0.9082483$ \\
			$14$ & $-0.9082483$ & $0.2958759$ & $0.2958759$ \\
			$15$ & $-0.2958759$ & $0.9082483$ & $0.2958759$ \\
			$16$ & $-0.2958759$ & $0.2958759$ & $-0.9082483$ \\
			$17$ & $-0.9082483$ & $0.2958759$ & $-0.2958759$ \\
			$18$ & $-0.2958759$ & $0.9082483$ & $-0.2958759$ \\
			$19$ & $-0.2958759$ & $-0.2958759$ & $0.9082483$ \\
			$20$ & $-0.9082483$ & $-0.2958759$ & $0.2958759$ \\
			$21$ & $-0.2958759$ & $-0.9082483$ & $0.2958759$ \\
			$22$ & $-0.2958759$ & $-0.2958759$ & $-0.9082483$ \\
			$23$ & $-0.9082483$ & $-0.2958759$ & $-0.2958759$ \\
			$24$ & $-0.2958759$ & $-0.9082483$ & $-0.2958759$ \\
			$25$ & $1.0000$ & $0.0000$ & $0.0000$ \\
			$26$ & $0.0000$ & $1.0000$ & $0.0000$ \\
			$27$ & $0.0000$ & $0.0000$ & $1.0000$ \\
			$28$ & $-1.000$ & $0.0000$ & $0.0000$ \\
			$29$ & $0.0000$ & $-1.000$ & $0.0000$ \\
			$30$ & $0.0000$ & $0.0000$ & $-1.000$ \\

			\hline\hline 
		\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabularx}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:A2}
			% 
			Raw intensities $I_k^*$ and scaled intensities $y_k$}
		\begin{tabular}{|c|c|c|c|c|c|c|}
			\hline\hline
			$\alpha$  & $I(\hat{\bf n}_\alpha\ ,\ 15^{\circ})$ &  $I(\hat{\bf n}_\alpha \ , \ 55^{\circ})$ &  $I(\hat{\bf n}_\alpha \ ,\ 90^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 15^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 55^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 90^{\circ})$ \\
		    \hline
			$1$ & $5.236437793$ & $0.008879799$ & $0.01023413$ & $-0.566323866$ & $-0.895169311$ & $-0.782655503$ \\
			$2$ & $9.029762808$ & $0.014176754$ & $0.023474524$ & $1.604434643$ & $-0.737872411$ & $1.16224444$ \\
			$3$ & $5.677784222$ & $0.018003042$ & $0.012268563$ & $-0.313760083$ & $-0.624248031$ & $-0.48381477$ \\
			$4$ & $4.054681384$ & $0.008596164$ & $0.007681417$ & $-1.242592777$ & $-0.903592052$ & $-1.157627171$ \\
			$5$ & $5.916429873$ & $0.012267124$ & $0.018806686$ & $-0.17719333$ & $-0.794580264$ & $0.47657917$ \\
			$6$ & $7.154962253$ & $0.040816852$ & $0.007678353$ & $0.531566054$ & $0.053224459$ & $-1.158077234$ \\
			$7$ & $4.857371303$ & $0.057897419$ & $0.009575087$ & $-0.78324749$ & $0.560444156$ & $-0.87946335$ \\
			$8$ & $9.018457316$ & $0.061837715$ & $0.027314068$ & $1.597964991$ & $0.677454091$ & $1.726240514$ \\
			$9$ & $5.001594138$ & $0.007138369$ & $0.009576248$ & $-0.700714897$ & $-0.946882332$ & $-0.879292708$ \\
			$10$ & $4.069312021$ & $0.041444603$ & $0.012267124$ & $-1.234220286$ & $0.071865963$ & $-0.484026249$ \\
			$11$ & $6.542222096$ & $0.050631978$ & $0.023474524$ & $0.180920933$ & $0.34469166$ & $1.16224444$ \\
			$12$ & $7.930714067$ & $0.10058846$ & $0.010228239$ & $0.975495811$ & $1.828185342$ & $-0.78352083$ \\
			$13$ & $5.236437793$ & $0.008879799$ & $0.01023413$ & $-0.566323866$ & $-0.895169311$ & $-0.782655503$ \\
			$14$ & $9.029762808$ & $0.014176754$ & $0.023474524$ & $1.604434643$ & $-0.737872411$ & $1.16224444$ \\
			$15$ & $5.677784222$ & $0.018003042$ & $0.012268563$ & $-0.313760083$ & $-0.624248031$ & $-0.48381477$ \\
			$16$ & $4.054681384$ & $0.008596164$ & $0.007681417$ & $-1.242592777$ & $-0.903592052$ & $-1.157627171$ \\
			$17$ & $5.916429873$ & $0.012267124$ & $0.018806686$ & $-0.17719333$ & $-0.794580264$ & $0.47657917$ \\
			$18$ & $7.154962253$ & $0.040816852$ & $0.007678353$ & $0.531566054$ & $0.053224459$ & $-1.158077234$ \\
			$19$ & $4.857371303$ & $0.057897419$ & $0.009575087$ & $-0.78324749$ & $0.560444156$ & $-0.87946335$ \\
			$20$ & $9.018457316$ & $0.061837715$ & $0.027314068$ & $1.597964991$ & $0.677454091$ & $1.726240514$ \\
			$21$ & $5.001594138$ & $0.007138369$ & $0.009576248$ & $-0.700714897$ & $-0.946882332$ & $-0.879292708$ \\
			$22$ & $4.069312021$ & $0.041444603$ & $0.012267124$ & $-1.234220286$ & $0.071865963$ & $-0.484026249$ \\
			$23$ & $6.542222096$ & $0.050631978$ & $0.023474524$ & $0.180920933$ & $0.34469166$ & $1.16224444$ \\
			$24$ & $7.930714067$ & $0.10058846$ & $0.010228239$ & $0.975495811$ & $1.828185342$ & $-0.78352083$ \\
			$25$ & $8.589197415$ & $0.039227387$ & $0.024433841$ & $1.352317814$ & $0.006024147$ & $1.303159911$ \\
			$26$ & $7.179988381$ & $0.037734463$ & $0.014278111$ & $0.545887442$ & $-0.038309302$ & $-0.188629493$ \\
			$27$ & $4.518783843$ & $0.045969647$ & $0.022162922$ & $-0.977006687$ & $0.206240387$ & $0.9695815$ \\
			$28$ & $8.589197415$ & $0.039227387$ & $0.024433841$ & $1.352317814$ & $0.006024147$ & $1.303159911$ \\
			$29$ & $4.635190763$ & $0.153655662$ & $0.02212562$ & $-0.910391959$ & $3.404054059$ & $0.964102078$ \\
			$30$ & $4.290255329$ & $0.010364637$ & $0.014275348$ & $-1.107783832$ & $-0.851075979$ & $-0.189035408$ \\
			\hline\hline 
			\multicolumn{7}{l}{\small *$I_k$ values are calculated using MSTM package.} \\
		\end{tabular}
	\end{center}
\end{table}
